---
title: "Homework1"
author: "Cheng-Han Yu"
date: "July 17, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(rmarkdown)
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data
```{r loaddata}
data <- read.csv("../Data/priemelDataReconstruction.csv", header = TRUE)
```

## Show the data
```{r showdata}
head(data)
```


## Plot the physiologic response (OV/BV) as a function of serum level.
```{r plot_response_serum}
plot(data$SerumLevelInNgPerMl, data$OV.BV,
     xlab = "serum", ylab = "physiologic response (OV/BV)")
```

## Describe the trend
The higher the serum level is, the lower the physiologic response is. It seems that the physiologic response and serum level are negatively correlated. 

## Logistic Regression
```{r logisticreg}
# create a binary variable
data$OV.BV.bin <- 0
data$OV.BV.bin[data$OV.BV > 2] <- 1
# View(data)
out <- glm(OV.BV.bin ~ SerumLevelInNgPerMl, 
           family = binomial(link = "logit"), data = data)
summary(out)

data2 <- data[data$SerumLevelInNgPerMl > 10, ]
out2 <- glm(OV.BV.bin ~ SerumLevelInNgPerMl, 
           family = binomial(link = "logit"), data = data2)
summary(out2)
```

The answer changes much if we restrict the set of patients to exclude those with serum values far from the target level (e.g., 10 nmol/L or less). I would trust the result that excludes higher serum level.

## Describe the fit in text. State what the coefficient values are inline, rounded to 3 decimal places.
The estimated coefficients of the first fit are `r round(coef(out)[1], 3)` and `r round(coef(out)[2], 3)`. The estimated coefficients of the second fit are `r round(coef(out2)[1], 3)` and `r round(coef(out2)[2], 3)`.

## Invoke the earlier plot chunk to set things up, and then superimpose the regression fit. 
```{r plot_addline}
<<plot_response_serum>>
abline(h = 2, col = "red")
```

## Use abline to add a horizontal line at your estimate of the serum level at which 97.5% of the people would have their requirements met.


```{r fig_level_intake, eval=FALSE, echo=FALSE}
iomreview <- read.csv("../Data/iomReview.csv")
iomreview <- iomreview[complete.cases(iomreview), ]
plot(iomreview$IOMIntake, iomreview$IOMLevel)
```
















